### 2021-10-13 plos_latex_template.tex
Rocío: Adding Sara's version of rule 10

This rule is a complement to all the other rules. It is important to have a bold vision and clear targets. Some parts might be defined as baseline assumptions that are not up for discussion. However, there will always be compromises. Ideal solutions that meet all our expectations are often not possible. Don't let the perfect be the enemy of good. As a team, this is a challenging journey. Very early on, we tried to recognize that our resources were limited (both in time of the organizing team but also in money). We had to let go of certain aspects that were important to many of us. For an inclusive conference, we need to avoid giving in because considering all aspects seems impossible and burning ourselves and the team out because considering all aspects is actually impossible.

>>>>

% This rule is a complement to all the other rules. It is important to have a bold vision and clear targets. Some parts might be defined as baseline assumptions that are not up for discussion. However, there will always be compromises. Ideal solutions that meet all our expectations are often not possible. Don't let the perfect be the enemy of good. As a team, this is a challenging journey. Very early on, we tried to recognize that our resources were limited (both in time of the organizing team but also in money). We had to let go of certain aspects that were important to many of us. For an inclusive conference, we need to avoid giving in because considering all aspects seems impossible and burning ourselves and the team out because considering all aspects is actually impossible.

For many people working with diversity, one typical aim is institutionalizing diversity (Ahmed 2012). However, our aim is also a symptom that diversity and equity are not part of institutions, academic societies, and conferences. This rule is about the process of making diversity and inclusion possible and a complement to all the other rules. We believe we need to be accountable and we need to aim for permanence. Institutionality comes from a set of norms, values, and priorities and these determine who is allowed and how (Ahmed 2012). Our long-term goal is to set new norms, values, and priorities based on diversity. Organizing a diverse conference is part of the process of change. However, we cannot do everything at one conference or a few of them. It is important to have a bold vision and clear targets. Keep in mind that ideal actions are often not possible and resources are limited (both time of the organizing team and money.

If from the beginning we set diversity goals and actions for the conference, we can use that to be transparent and, later, accountable. Assess whether equity and inclusion goals were met during the meeting. This can be done internally within the organizing team and often also through the conference’s participants. Plan, balance and keep working to improve inclusion in the next edition of the conference. Try to propose permanent data collection to assess whether diversity and inclusion are actually being seen at the conference. We know that diversity and equity are not institutionalized, in fact, the system works to stop those who are changing the system (Ahmed 2019). We will find resistance, but diversity is a school. We also learn more about how people are being excluded, we learn that there are actions we can take to include more, and then, we can set higher goals on how to make inclusion possible.
